---
title: "HW 1"
subtitle: "Data 180, Professor Bilen"
author: 
  name: "Your Name"
  email: "XXXX@dickinson.edu"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document
---
Make sure that you have accepted the hw invitation link, and working with your clone repository.

**Due date:** September 19 beginning of class.

**Reminder:** You can insert R code in your Rmd file as a chunk in the following way:
```{r}
# Your code goes here
```
Make sure to insert a chunk for each (sub)section of the assignment.

## Preliminary Task
Go to [datacamp.com](https://datacamp.com) and complete the tutorial "Introduction to R".


## Task 1
a) Store the data below in a data frame object named `my_df`.


|Person | Preference|
|:------|:----------|
|Alice | Twitter |
| Bob | Facebook |
| Charlie | Twitter |
| Denise | Instagram |
| Erin | Facebook |
| Frank | Twitter |
| Gisele | Twitter |
| Harry | Instagram |
```{r}
Person <- c('Alice','Bob','Charlie','Denise','Erin','Frank','Gisele','Harry')
Preference <- c('Twitter','Facebook','Twitter','Instagram','Facebook','Twitter','Twitter','Instagram')


my_df=data.frame(Person,Preference)
my_df
```
b) What are the dimensions of `my_df`?
The data frame has a dimension of 2x8

c) Write R code that counts the total number of users.
```{r}
print(nrow(my_df))
```

d) Write R code that counts the total number of users who prefer Twitter.
```{r}
Twitter_person<-0
for (i in my_df$Preference ){
  if (i=="Twitter"){
    Twitter_person=Twitter_person+1
  }
}
Twitter_person
```
e) Write R code that returns what Gisele prefers.
```{r}
find_interest <- function(person_name) {
  location <- 0
  
  for (name in my_df$Person) {
    location <- location + 1
    
    if (name == person_name) {
      return(my_df[location, "Preference"])
    }
    
    if (location > nrow(my_df)) {
      return('not found')
    }
  }
}
print(find_interest('Gisele'))
```

## Task 2
a) Create a vector named `my_vec` that includes all integers from 1 to 10 (inclusive).
```{r}
my_vec <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)
```

b) Replace the second element in `my_vec` with the number `99`.
```{r}
my_vec[2]<-(99)
```
c) Write a function called `my_func` that prints `This element is greater than 5!` if an element in `myvec` is greater than 5, and `This element is NOT greater than 5!` otherwise.
```{r}
my_func <- function(vec) {
  for (element in vec) {
    if (element > 5) {
      print("This element is greater than 5!")
  }
    else {
      print("This element is NOT greater than 5!")
    }
  }
}
my_func(my_vec)
```

## Task 3
a. Write a function named `get_fibonacci` that returns the n'th value in the [fibonacci sequence]( ). For example, `get_fibonacci(5)` should return 5; `get_fibonacci(7)` should return 13 and so on. ***Hint:** It is possible to call the same function from inside it. E.g., you can call `get_fibonacci()` from inside `get_fibonacci()`. Like the movie inception!*
```{r}
get_fibonacci <- function(n) {
  if (n <= 0) {
    stop("Input must be a positive integer.")
  }
  
  if (n == 1) {
    return(0)
  } 
  else if (n == 2) {
    return(1)
  } 
  else {
    return(get_fibonacci(n - 1) + get_fibonacci(n - 2))
  }
}
```
b. Let's see R's computational power. Using your function in part (a), find and return the 19th value in the fibonacci sequence.
```{r}
get_fibonacci(19)
```

<br>
You are done! 🏁 Don't forget to `commit` and `push` your .Rmd file to your Github clone repository before the due date.
<br>

